\documentclass[11pt,a4paper,sans]{moderncv}        % font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', ...) and font family ('sans' and 'roman')

%-------------------------------------------------------------------------------
% ModernCV theme settings
%-------------------------------------------------------------------------------
\moderncvstyle{banking}                            % style: 'casual' (default), 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}                              % color: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'
% \renewcommand{\familydefault}{\sfdefault}       % Uncomment to use sans serif font
% \nopagenumbers{}                                % Uncomment to suppress automatic page numbering for CVs longer than one page

%-------------------------------------------------------------------------------
% Encoding and fonts
%-------------------------------------------------------------------------------
\usepackage[utf8]{inputenc}

%-------------------------------------------------------------------------------
% Page margins
%-------------------------------------------------------------------------------
\usepackage[scale=0.9,bottom=0.4in,top=0.5in]{geometry}
% \setlength{\hintscolumnwidth}{3cm}             % Change width of the dates column
% \setlength{\makecvtitlenamewidth}{10cm}        % Force the width allocated to your name (classic style)

%-------------------------------------------------------------------------------
% Personal data
%-------------------------------------------------------------------------------
\name{Sheshansh}{Agrawal}
% \title{Curriculum Vitae}
% \address{Senior Applied Scientist, Microsoft}{}{}
% \homepage{www.sheshansh.com}

%---  Extra info line -----------------------------------------------------------
%  Replaced icon macros with plain text links for faster compilation.
\extrainfo{\email{sheshanshagrawal@gmail.com}{sheshanshagrawal@gmail.com} \textbar{} 
  \href{http://www.sheshansh.com}{Website} \textbar{} 
  \href{https://scholar.google.com/citations?user=5h8jXlxko_oC}{Google~Scholar} \textbar{} 
  \href{https://twitter.com/sheshanshag}{Twitter} \textbar{} 
  \href{https://www.linkedin.com/in/sheshansh-agrawal-b5a79b97/}{LinkedIn}}
% \phone{+1(425)-591-2534}
% \photo[64pt][0.4pt]{picture}
% \quote{Some quote}

%-------------------------------------------------------------------------------
% Content
%-------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-25pt}

%-----       EXPERIENCE       ---------------------------------------------------
\section{Experience}
\textbf{Tech Lead Manager, Retrieval Research}, Contextual AI \hfill \textit{Jun 2024 -- Present}
\begin{itemize}
  \item Leading research on retrieval, reranking, text-to-SQL, and their applications in search agents.
  \item Launched SoTA and the first commercial instruction‑following relevance reranking model (\href{https://contextual.ai/blog/introducing-instruction-following-reranker/}{Blog}, \href{https://x.com/douwekiela/status/1899490844572577958}{Tweet}, \href{https://apnews.com/press-release/pr-newswire/contextual-ai-launches-worlds-first-instruction-following-reranker-ecb56585dc31bee5968c13d7000f30b3}{AP~News}, \href{https://seekingalpha.com/pr/20030352-contextual-ai-launches-worlds-first-instruction-following-reranker}{Seeking~Alpha}).
  \item Built a SoTA text‑to‑SQL agent, which topped the \href{https://bird-bench.github.io/}{BIRD‑Bench} leaderboard (\href{https://x.com/apsdehal/status/1895561744120234399}{Tweet}, \href{https://www.linkedin.com/feed/update/urn:li:activity:7301377754749353984/}{LinkedIn}).
  \item Built an agentic alternative to GraphRAG in the pursuit of enabling search agents to exploit graphical structure which is available in some domains.
  \item Published a faster LLM ranking algorithm BLITZRANK using tournement graphs, which was better than previous methods while being 25-40\% more token efficient.
  \item Built DeepSearch style agents on enterprise data. Worked on orchestration, building environments, RL infrastructure.
  \item Worked on ReAct style dynamic agent integration for our Agent Composer product.
\end{itemize}
\vspace{5pt}

\textbf{Senior Applied Scientist}, Microsoft Bing Ads \hfill \textit{Mar 2022 -- May 2024}
\begin{itemize}
  \item Built and led language models for multi‑modal embedding‑based selection (dense retrieval) at Microsoft advertising.
  \item Designed and implemented \emph{CORGEE} -- a large‑scale contrastive‑learning infrastructure for training embeddings at scale (C\#, Scope, SQL, Cython, Numba, Cnpy, PyTorch, Flash‑attention, DeepSpeed; up to 256 GPUs with high utilisation).
  \item Worked on OOD‑DiskANN to improve out‑of‑domain generalization of ANNS indexing algorithms.
\end{itemize}
\vspace{5pt}

\textbf{Research Engineer}, Microsoft Research India \hfill \textit{Aug 2019 -- Mar 2022}
\begin{itemize}
  \item Built and published the first technique for personalised dense retrieval: \textbf{XPERT}.
  \item Developed extreme‑classification algorithms with label features (\emph{DECAF} and \emph{ECLARE}) that train representations and the item index jointly end‑to‑end.
\end{itemize}

%-----       EDUCATION       ----------------------------------------------------
\vspace{-5pt}
\section{Education}
\textbf{B.Tech. (Hons.) in Computer Science and Engineering} \hfill \textit{2015--2019}\\
Indian Institute of Technology Bombay, Mumbai, India \hfill \textit{CGPA: 9.68/10}\\
\textit{Minor:} Applied Statistics and Informatics\\
Department Rank: 3/123

%-----       PUBLICATIONS       --------------------------------------------------
\vspace{-5pt}
\section{Publications}
\begin{itemize}
  \item \textbf{OOD‑DiskANN}: Efficient and scalable graph ANNS for out‑of‑distribution queries -- Preprint.\\
        \textit{S. Jaiswal, R. Krishnaswamy, A. Garg, H.V. Simhadri, Sheshansh Agrawal}
  \item \textbf{XPERT}: Personalised Retrieval over Millions of Items -- \textit{SIGIR 2023}.\\
        \textit{H.~Vemuri*, Sheshansh Agrawal*, S.~Mittal*, D.~Saini, A.~Soni, M.~Varma}
  \item \textbf{ECLARE}: Extreme classification with label graph correlations -- \textit{WWW 2021}.\\
        \textit{A.~Mittal, N.~Sachdeva, Sheshansh Agrawal, S.~Agarwal, P.~Kar, M.~Varma}
  \item \textbf{DECAF}: Deep extreme classification with label features -- \textit{WSDM 2021}.\\
        \textit{A.~Mittal, K.~Dahiya, Sheshansh Agrawal, D.~Saini, S.~Agarwal, P.~Kar, M.~Varma}
  \item Lexicographic ranking supermartingales: an efficient approach to termination of probabilistic programs -- \textit{POPL 2018}.\\
        \textit{Sheshansh Agrawal, K.~Chatterjee, P.~Novotný}
\end{itemize}

%-----       AWARDS & POSITIONS       -------------------------------------------
\vspace{-5pt}
\section{Awards and Positions}
\begin{itemize}
  \item \textbf{FY23 Q4, FY21 Q4 Engineering Excellence Award}, Microsoft Ads.
  \item Medals for India at International Olympiads:
    \begin{itemize}
      \item Silver -- International Physics Olympiad, Mumbai (2015)
      \item Gold -- International Olympiad in Astronomy \& Astrophysics, Suceava (2014)
      \item Bronze -- International Olympiad in Astronomy \& Astrophysics, Volos (2013)
      \item Silver -- International Astronomy Olympiad, Seoul (2012)
    \end{itemize}
  \item \textbf{Institute Academic Award}, IIT Bombay (2016)
  \item Ranked 4 / 1.4 million candidates in JEE Mains, 2015 (India‑wide).
  \item Elected General Secretary, Computer Science Department Association (2018--19)
\end{itemize}

%-------------------------------------------------------------------------------
\end{document}
